Vragenlijst thesis evaluatie

### 2015-02-15 doc/template/chap-1.tex
tadaa

\section{Intro Game Theory}

%begin over dat gametheorie handig is in de economie
In the following paragraph an introduction to game theory is given based on the work of \todo{werk van Essentials of Game Theory} and \todo{Coursera game theory}.
Game theory studies the interaction between independent and self-interested agents. For this reason it is very important for economics and also for politics, biology, computer science, philosophy and a variety of other disciplines. It is a mathematical way of modelling the interactions between two or more agents where the outcome depends on what everybody does and how it should be structured to lead to good outcomes. \\
%Every agent has different levels of happiness for the different outcomes.
A self-interested independent agent does not necessarily mean that they want to harm other agents or that they only care about themselves. Each agent has preferences about the states of the world he likes. These preferences are mapped to natural numbers and are called the utility function. The numbers are interpreted as a mathematical measure to tell you how much an agent likes or dislikes the states of the world. It also explains the impact of uncertainty. When an agent is uncertain about a distribution of outcomes, his utility will describe the expected value of the utility function with respect to the probability of the distribution of the outcomes. For example: with 0.7 probability it will be 7 degrees outside and 0.3 probability it will be 10 degrees. The agent can have a different opinion about that distribution versus another distribution. (\todo{uitleggen aan de hand van een voorbeeld}).\\

A game in game theory consists of multiple agents and every agent has a set of actions that he can play. 
%self interested meaing

%utility function meaning

%Cooperative and non cooperative games

% example of a game

@@

\section{Virusses}

@@

\section{Conclusion}
The final section of the chapter gives an overview of the important results
of this chapter. This implies that the introductory chapter and the
concluding chapter don't need a conclusion.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%			Introduction Chapter 1				%%%%%%
%%%%%												%%%%%%
%%%%%												%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the following paragraph an introduction to game theory is given based on the work of \todo{werk van Essentials of Game Theory} and \todo{Coursera game theory}. Voor een meer gedetailleerdere intro ook dit book.
%------------------------------------------------%
%            Intro Game Theory 					 %
%------------------------------------------------%
\section{Intro Game Theory}
\label{Cha:1:Intro.Game.Theory}

%begin over dat gametheorie handig is in de economie

Game theory studies the interaction between independent and self-interested agents. For this reason it is very important for economics and also for politics, biology, computer science, philosophy and a variety of other disciplines. It is a mathematical way of modelling the interactions between two or more agents where the outcome depends on what everybody does and how it should be structured to lead to good outcomes. \\
%Every agent has different levels of happiness for the different outcomes.
%self interested meaning
A self-interested independent agent does not necessarily mean that they want to harm other agents or that they only care about themselves. 
%utility function meaning
Each agent has preferences about the states of the world he likes. These preferences are mapped to natural numbers and are called the utility function. The numbers are interpreted as a mathematical measure to tell you how much an agent likes or dislikes the states of the world. It also explains the impact of uncertainty. When an agent is uncertain about a distribution of outcomes, his utility will describe the expected value of the utility function with respect to the probability of the distribution of the outcomes. For example: with 0.7 probability it will be 7 degrees outside and 0.3 probability it will be 10 degrees. The agent can have a different opinion about that distribution versus another distribution. (\todo{uitleggen aan de hand van een voorbeeld}).\\
%Cooperative and non cooperative games
In a decision game theoretic approach an agent will try to act in such a way to maximise his expected or average utility function. It becomes more complicated when two or more agents want to maximise their utility and whose actions can affect each other utilities. This kind of games are referred to as non cooperative game theory, where the basic modelling unit is the group of agents. The individualistic approach, where the basic modelling is only one agent, is referred as cooperative game theory.

In the following list a couple of terms that will be used throughout the paper.
\begin{description}
\item \textit{Players}: players are referred as the ones who are the decision makers. It can be a person, a company or an animal.
\item \textit{Actions}: actions are what the player can do. 
\item \textit{Outcomes}:  
\item \textit{Utility function}: the utility function is the mapping of the level of happiness of an agent about the state of the world to natural numbers.
\item \textit{Strategies}: A strategy is the combination of different actions. A pure strategy is only one action.
\end{description}

A game in game theory consists of multiple agents and every agent has a set of actions that he can play.

% --------------- example of a game -----------------%

@@

%------------------------------------------------%
%            Intro about virusses				 %
%------------------------------------------------%
\section{Virusses}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%			Conclusion Chapter 1				%%%%%%
%%%%%												%%%%%%
%%%%%												%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{Cha:1:Conclusion}
The final section of the chapter gives an overview of the important results
of this chapter. This implies that the introductory chapter and the
concluding chapter don't need a conclusion.
